# Install + load packages

```{r}
#install.packages(c("devtools", "usethis", "roxygen2"))
library(devtools)
library(usethis)
library(roxygen2)
```
# move to package directory
```{r}
setwd("~/R_packs/ryotaro/")
```

# Following commands will be used in R console as you go through the package creating process.

## 1 name your package and set path, this opens up new Positron 
```{r}
usethis::create_package("~/R_packs/ryotaro")
```

## 2 make a funciton file under /R
```{r}
usethis::use_r("function_name")
```

## 3 Write a function under that R file

## 4 Register knitr as a dependent of package　
### Do this if your function uses other functions inside.
```{r}
usethis::use_package("package_name")
```
## 5 make a documentation　# 6 then install　
```{r}

#While editing, do
devtools::load_all()

#Do this to update
devtools::document()


#after making changes, restart R then
devtools::install()
```

### when editing theme_ryotaro, run follwing in terminal to preview your theme
```{bash}
Rscript -e 'pkgload::load_all(".", export_all = TRUE, quiet = TRUE); library(ggplot2); 
p <- ggplot(mtcars, aes(wt, mpg, color = factor(cyl))) + geom_point(size = 3, alpha = 0.9) + 
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.8) + scale_color_ryotaro(name = "Cylinders") + 
  labs(title = "theme_ryotaro preview", subtitle = "mtcars: weight vs mpg", x = "Weight", y = "Miles per gallon") + 
  theme_ryotaro(base_size = 13); ggplot2::ggsave("theme_ryotaro_preview.png", p, width = 7, height = 4.5, dpi = 160)'
```
